Mixture Modeling Paper Results

### 2017-03-09 PaperEx170308.Rmd
results for paper

```{r loadfunctions}
library(mixsmsn)
library(sn)
#-----------------------------------------------
#[IC] Load Functions
#-----------------------------------------------

@@

fitloopsobject<-fitloops(datawithids=examp2)
#might not run, if it doesn't, then load the full file: 
load(file="/Users/sarahsullivan/Documents/SullivanDocs/Rwd/cutoff/ex2fitloops")
fitloopsobject<-ex2
bestfitsobject<-bestfits(fitres=fitloopsobject)
bicgraph(model=bestfitsobject)

@@

```{r while loop}

>>>>

```{r set_knitr_chunk_options, echo = F, warning=F, message=F}
rm(list = ls())

library(knitr)
library(markdown)
opts_chunk$set(message=FALSE, echo = F,
               warning = F,fig.height = 5, fig.width = 10, tidy = F)

#Work
#opts_knit$set(root.dir = "C:/Users/ntdintern/Google Drive/Sarah Sullivan/Code")
#School
#opts_knit$set(root.dir = "H:/TFGH/Code")
#Laptop
opts_knit$set(root.dir = "/Users/sarahsullivan/Google Drive/Sarah Sullivan/Code")
```

```{r loadfunctions, echo=F, warning=F, message=F}
library(mixsmsn)
library(sn)
#-----------------------------------------------
#[IC] Load Functions
#-----------------------------------------------

@@

#fitloopsobject<-fitloops(datawithids=examp2)
  #might not run due to 5 component solution not being easily optimized, if it doesn't run, either load the full file, or run fitloopsobject<-fitloops(datawithids=examp2,maxcp=4): 
load(file="/Users/sarahsullivan/Documents/SullivanDocs/Rwd/cutoff/ex2fitloops")
fitloopsobject<-ex2

bestfitsobject<-bestfits(fitres=fitloopsobject)
bicgraph(model=bestfitsobject)

@@

```{r while loop, echo=F}
